Estimation below the detection limit with application to cryo-EM

### 2018-08-15 TEX/inverse_problem_draft.tex
Revised Appendix C. Several open questions remained

For $K=1$, our problem can be interpreted as a special case of the system identification problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
%
\begin{math}
%
y = x\ast w + \varepsilon,  
%
\end{math} 
%
where $x$ is the unknown signal (the ``system''), $w$ is an unknown, random, input sequence, and $\varepsilon$ is an additive noise.   
%The problem has also been studied in the case of a known input $w$~\cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}. 
The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}. In the special case where $w$, satisfying one of the generative models above, we obtain our model in the  case of a single signal ($K = 1$). The same observation model is used for blind deconvolution, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few. 
%\TODO{ref this by Giannakis: \cite{giannakis1989identification}}

@@

@@

Should we devote a whole section for EM or merge it with the next one?

@@

\TODO{The following was copying from the Methods section}

>>>>

For $K=1$, our problem can be interpreted as a special case of the \emph{system identification} problem. Similarly to~\eqref{eq:model}, the system identification forward model takes the form
%
\begin{math}
%
y = x\ast w + \varepsilon,  
%
\end{math} 
%
where $x$ is the unknown signal (the ``system''), $w$ is an unknown, random, input sequence, and $\varepsilon$ is an additive noise.   
%The problem has also been studied in the case of a known input $w$~\cite{pillonetto2010new,dinuzzo2015kernels,bottegal2016robust}. 
The goal of this problem is to estimate $x$, usually referred to as ``identifying the system.'' The question of identifiability of $x$ under this observation model is addressed for certain Gaussian and non-Gaussian $w$ in~\cite{benveniste1980robust,kormylo1983identifiability}. In the special case where $w$, satisfying one of the generative models above, we obtain our model in the  case of a single signal ($K = 1$). The same observation model is used for blind deconvolution, a longstanding problem arising in a variety of engineering and scientific applications such as astronomy, communication, image deblurring, system identification and optics; see~\cite{jefferies1993restoration,shalvi1990new,ayers1988iterative,abed1997blind}, just to name a few. 
%\TODO{ref this by Giannakis: \cite{giannakis1989identification}}

@@

\subsection{The multiple signals case}

@@

Suppose we extract a set of windows $y_1,\ldots,y_q$ windows of $y$. If the signal's occurrences are sufficiently separated, then we can model each window as 
\begin{equation} \label{eq:EM}
y_i = PR_{r_i}Zx + \varepsilon,
\end{equation}
where $Zx = (0,\ldots 0,x[0],\ldots,x[L-1])\in\mathbb{R}^{2L}$, $R_r$ shifts a signal cyclically by $r$ entries  and $P$ restricts a signal to its first $L$ entries. We assume the distribution of $R_r$ to be of the form $\rho = (\alpha,\frac{1-\alpha}{2L-1},\ldots,\frac{1-\alpha}{2L-1})\in\Delta^{2L}$. Namely, the probability to see no signal (only noise) is $\alpha$, whereas there is equal probability to observe each one of the possible signal fractions.

If each window was drawn independently from this model, then it is straight-forward to derive the EM formulation, similarly to~\cite{bendory2017bispectrum,abbe2017multireference}. In particular, ....

Indeed, the formulation~\eqref{eq:EM} does not follow the EM recipe since, in order to keep the separation constraint, the random shifts $R_r$ are correlated across windows. Nonetheless, numerically it seems that the EM method works well; see Section TKTK for numerical demonstrations.

@@
